---
title: "Final_Proj"
author: "Rithu Uppalapati"
date: "12/7/2020"
output: html_document
---

###  Iron Deficiency differences in Race and Gender 

```{r}
library(tidyverse)
setwd("/Users/rithuuppalapati/Desktop/stats506/Final_Project")
library("foreign")
demo <- read.xport("DEMO_J.XPT")
fertin <- read.xport("FERTIN_J.XPT")
demo <- merge(demo, fertin, by = "SEQN")
```


Research Question: Are women more likely to have iron deficiency's when compared to men, and does it occur in specific races differently?

A ferritin test measures the amount of ferritin in your blood. Fertin is a blood protein that contains iron. A ferritin test helps your doctor understand how much iron your body stores.

The Mayo Clinic says that fertin levels <11 micrograms per liter in women and <24 micrograms per liter in men are indicative of iron deficiency 

* To - Do: 
  + Separate into two groups for each gender: 
    - Group 1 - Normal Fertin Levels
    - Group 2 - Low Fertin Levels 
  + Control for diet and age
  
```{r}
demo$M_Iron <- ifelse(demo$RIAGENDR == 1 & demo$LBDFERSI < 24, 1, 0)
demo$F_Iron <- ifelse(demo$RIAGENDR == 2 & demo$LBDFERSI < 11, 1, 0)
```


### Iron Deficiency Difference in Gender 

```{r}
library(survey)
nhanes_design <- svydesign(id = ~SDMVPSU, strata = ~SDMVSTRA, weights = ~WTINT2YR, nest = TRUE, data = demo)
iron_levels <- subset(nhanes_design, M_Iron == 1 || F_Iron == 1)
svymean(~RIAGENDR, iron_levels, na.rm = TRUE)
```


Use Survey Package 
* To-Do
  + Univariate logistic regression between gender because I am coding Ferritin Levels into a dummy variable
  + Use surveymeans() in order to compare proportions
  + determine if differences between men and women are statistically significant 
  + Create boxplot to show distribution of ferritin levels between men and women 
  
### Iron Deficiency Differences in Race

Use Survey Package
* To-DO
  + multivariate logistic regression with race 
  + group for gender if the results are significant
  + Create histograms by race to show proportion of iron deficiency